Integrating spatial and temporal patterns in ecological forecasts

### 2018-07-02 doc/manuscript.tex
Started community example write-up

\graphicspath{ {./../genetic-diversity/figures/} }

@@

%\newpage
%\renewcommand{\refname}{Literature cited}
%\bibliographystyle{Ecology}
%\bibliography{RemovalRefs}

>>>>

\graphicspath{ {./../genetic-diversity/figures/} {./../community-turnover/figures/} }

@@

\subsection{Community turnover example}

In the previous example, evolutionary change was the slow process whose rate determined the shift in weight from the temporal to spatial forecast of the state of a population. The process of compositional turnover--change in the abundances and identities of species interacting at a site--can have a similar effect at the community level. We demonstrate this using a metacommunity model developed by Alexander et al. (ref). 
%\newpage
%\renewcommand{\refname}{Literature cited}
%\bibliographystyle{Ecology}
%\bibliography{RemovalRefs}
